### 2017-04-02 paper/evaluation.tex
fixing rq4 methodology

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
\Luis{rework this... $\rightarrow$}To reduce the number of build files
to inspect, we consider only \pomf{} files that contain the
configuration node inside a \CodeIn{plugin} tag with a child tag named
\CodeIn{artifactId} with the content \CodeIn{maven-surefire-plugin}.
This mining step, however, is not sound as a matching project may not 
indicate a project with a valid configuration for running tests in parallel.
\Comment{
False positive can happen because of comments, for instance.  
To eliminate the cases of false positives and also to categorize 
true positive cases, we complemented the initial mining step with a 
manual inspection of files.
}
%% settings); the second step (inspection) consists in a manual
%% inspection to confirm the presence of parallelism settings in the
%% build file and classify them according to the parallelism level.
%% Figure \Fix{removed} describes the discovery step: we list the paths
%% of all build files and filter only the files that contain any of the

Figure~\ref{tab:inspection-table} summarizes our results. The first
column indicates the group of projects according to their time cost.
The second column indicates the number of build files per group.  The
third column is a subset from the previous column and represents the
number of build files found in the mining step (including
false-positives highlighted in parentheses). The last column indicates
the ratio of projects with parallelization settings.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
    \caption{\label{fig:freqmodes-static}Distribution of parallel modes
    identified statically in a subset of \numProjectsPar{} projects.
    A project may have support to more than one parallel mode.}
\end{figure}

>>>>

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
\Luis{rework this... $\rightarrow$}To reduce the number of build files
to inspect, we consider only \pomf{} files that contain
\CodeIn{plugin} tags with a child tag \CodeIn{artifactId} with the
value \CodeIn{maven-surefire-plugin} and a \CodeIn{configuration}
node. This mining step, however, is not sound as a matching project may not 
indicate a project with a valid configuration for running tests in parallel.

%False positive can happen because of comments, for instance.  
%To eliminate the cases of false positives and also to categorize 
%true positive cases, we complemented the initial mining step with a 
%manual inspection of files.
%% settings); the second step (inspection) consists in a manual
%% inspection to confirm the presence of parallelism settings in the
%% build file and classify them according to the parallelism level.
%% Figure \Fix{removed} describes the discovery step: we list the paths
%% of all build files and filter only the files that contain any of the

Figure~\ref{tab:inspection-table} summarizes our results. The first
column indicates the group of projects according to their time cost.
The second column indicates the number of build files per group. 
The last column indicates the ratio of projects with parallelization settings.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes-static.pdf}
	\caption{\label{fig:freqmodes-static}\Luis{This is wrong, it
	should be \textbf{CF0} instead of \textbf{CL0}}Distribution of parallel modes
    identified statically in a subset of \numProjectsPar{} projects.
    A project may have support to more than one parallel mode.}
\end{figure}
